---
title: "Coursera - Persentation Developing Data Products"
author: "Mochamad Gilang Saputra"
date: "January 31, 2020"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction
This map will take you to search for the country you are looking for

## How It Works
- The application is written in Shiny which is a web application framework for R
- The source code consists of two files: **server.R** and **ui.R**
- **server.R** includes the the server logic of a Shiny web application
- **ui.R** includes the the user-interface definition, which uses the sidebarLayout template
- The application leverages the **maps** and **mapdata** libraries for displaying the map
- The application is hosted on Rstudio's shiny server in the cloud (Shinyapps.io)

## Documentation
- Maps in R
  
```{r}
library(maps)
library(mapdata)
library(ggplot2)
states <- map_data("world2")

ggplot(data = states) + 
  geom_polygon(aes(x = long, y = lat, fill = region, group = group), color = "white") + 
  coord_fixed(1.3) +
  guides(fill=FALSE)  # do this to leave off the color legend
```


## Link
- Application URL: https://mgilangs.shinyapps.io/finalproject_developing_data_products/
- Github Repository URL: https://github.com/mgilangs/FInal-Project-Developing-Product